---
title: "assignemnt 04"
author: "chen wei"
date: "2022-10-05"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(httr)
library(tidyverse)
library(stringr)
library(tidytext)
library(parallel)
```
## FIRST PART(UNFINSHED AND CONFUSED)
Problem 1: Make sure your code is nice
```{r}
# Total row sums
fun1 <- function(mat) {
  n <- nrow(mat)
  ans <- double(n) 
  for (i in 1:n) {
    ans[i] <- sum(mat[i, ])
  }
  ans
}
dat <- matrix(rnorm(200 * 100), nrow = 200)

fun1alt <- function(mat) {
  # YOUR CODE HERE
rowSums(mat)
  }

fun1(dat)
```
```{r}
# Use the data with this code
set.seed(2315)
dat <- matrix(rnorm(200 * 100), nrow = 200)

# Test for the first
microbenchmark::microbenchmark(
  fun1(dat),
  fun1alt(dat)
)
```
```{r}
# Cumulative sum by row
fun2 <- function(mat) {
  n <- nrow(mat)
  k <- ncol(mat)
  ans <- mat
  for (i in 1:n) {
    for (j in 2:k) {
      ans[i,j] <- mat[i, j] + ans[i, j - 1]
    }
  }
  ans
}
fun2(dat)
```
```{r}
fun2alt <- function(mat) {
  # YOUR CODE HERE
t(apply(mat,1,cumsum))
  }


# Use the data with this code
set.seed(2315)
dat <- matrix(rnorm(200 * 100), nrow = 200)



# Test for the second
microbenchmark::microbenchmark(
  fun2(dat),
  fun2alt(dat)
)
```
Problem 2: Make things run faster with parallel computing
```{r}
sim_pi <- function(n = 1000, i = NULL) {
  p <- matrix(runif(n*2), ncol = 2)
  mean(rowSums(p^2) < 1) * 4
}

# Here is an example of the run
set.seed(156)
sim_pi(1000) # 3.132
```
```{r}
# This runs the simulation a 4,000 times, each with 10,000 points
set.seed(1231)
system.time({
  ans <- unlist(lapply(1:4000, sim_pi, n = 10000))
  print(mean(ans))
})
```
```{r}
# YOUR CODE HERE
system.time({
  # YOUR CODE HERE
  ans <- unlist(lapply(1:4000, sim_pi, n = 10000))
  # YOUR CODE HERE
  print(mean(ans))
  # YOUR CODE HERE
})
```
```{r}
library(parallel)
system.time({
  cl <- parallel::makePSOCKcluster(2L)
  parallel::clusterSetRNGStream(cl, 123) # Make sure it is reproducible!
    ans <- parLapply(cl,1:4000, sim_pi, n = 10000)
    print(mean(unlist(ans)))
    parallel::stopCluster(cl)
})
```
## second part
```{r}
# install.packages(c("RSQLite", "DBI"))

library(RSQLite)
library(DBI)

# Initialize a temporary in memory database
con <- dbConnect(SQLite(), ":memory:")

# Download tables
film <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film.csv")
film_category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/film_category.csv")
category <- read.csv("https://raw.githubusercontent.com/ivanceras/sakila/master/csv-sakila-db/category.csv")

# Copy data.frames to database
dbWriteTable(con, "film", film)
dbWriteTable(con, "film_category", film_category)
dbWriteTable(con, "category", category)
dbListTables(con)
```
```{r}
dbGetQuery(con, "PRAGMA table_info(category)")
```


```{sql, connection=con, output.var = "x1"}
PRAGMA table_info(film)
```

Question 1
How many many movies is there avaliable in each rating catagory.
```{r}
Q1<-dbGetQuery(con,"
SELECT   rating,
COUNT(*) AS number
FROM    film
GROUP BY rating
           ")
Q1
```
Question 2
What is the average replacement cost and rental rate for each rating category.
```{r}
Q2_1<-dbGetQuery(con,"
SELECT  rating, replacement_cost,
COUNT(*) AS count,
AVG(replacement_cost) AS replacement_cost_mean
FROM film
GROUP BY rating
           ")
Q2_1
Q2_2<-dbGetQuery(con,"
SELECT  rating, rental_rate,
COUNT(*) AS count,
AVG(rental_rate) AS rental_rate_mean
FROM  film
GROUP BY rating
           ")
Q2_2

```
```{r}
Q2<-merge(Q2_1, Q2_2, by.x = "rating", by.y = "rating", all = TRUE)
Q2
```
Question 3
Use table film_category together with film to find the how many films there are with each category ID?
```{r}
Q3<-dbGetQuery(con,"
SELECT  film.film_id, film_category.category_id,
COUNT(*) AS number
FROM film
INNER JOIN film_category  ON film.film_id = film_category.film_id
GROUP BY category_id
")
```
Question 4
Incorporate table category into the answer to the previous question to find the name of the most popular category.
```{r}
Q4<-dbGetQuery(con,"
SELECT  film.film_id, film_category.category_id,category.category_id, category.name,
COUNT(*) AS N
FROM film
INNER JOIN film_category  ON film.film_id = film_category.film_id
INNER JOIN category ON category.category_id = film_category.category_id
GROUP BY name 
")
Q4
```
the sport movie is most popular